---
title: "Stream Clustering Algorithms"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```


## Clustream vs Denstream

The Clustream algorithm assumes the clusters are spherical in nature, so it performs poorly when the clusters have arbitrary shapes. Denstream overcomes this limitation since it uses a version of DBSCAN as the offline clustering algorithm.

We are going to simulate a stream with 3 clusters consisting of 2-dimensional points. 

Plotted below is a sample of 500 points from the stream. We can see that there are 2 natural clusters and they are not circular.




## Clustream 

After running the Clustream algorithm with 50 microclusters, the points are summarized with microclusters

```{r clustream1}
library("streamMOA")

stream <- DSD_Gaussians(k=3, d=2, noise=0.05)

# cluster with CluStream
clustream <- DSC_CluStream(m=50)
update(clustream, stream, 500)
clustream
# plot micro-clusters
plot(clustream, stream)

```


This plot shows the assignment area (radii) of the Micro-Clusters
```{r clustream2}
# plot assignment area (micro-cluster radius)
plot(clustream, stream, assignment=TRUE, weights=FALSE)

```



In the offline phase, the following clusters are found by K-Means
```{r clustream3}
# reclustering. Use weighted k-means for CluStream
kmeans <- DSC_Kmeans(k=3, weighted=TRUE)
recluster(kmeans, clustream)
plot(kmeans, stream, type="both")

```

## Denstream

Now we will use Denstream to cluster the same set of points. We notice that Clustream has included a few outliers in its final clustering result, wheras Denstream has correctly removed outliers, and was also able to find arbitrary shaped clusters.  

```{r denstream1, warning=FALSE, message=FALSE}
denstream <- DSC_DenStream(epsilon=0.05)
update(denstream, stream, 500)
plot(denstream, stream, type="both")

```